%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PlushCV - One Page Two Column Resume
% LaTeX Template
% Version 1.0 (11/28/2021)
%
% Author:
% Shubham Mazumder (http://mazumder.me)
%
% Hacked together from:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Figure out a smoother way for the document to flow onto the next page.
% 3. Add more icon options 
% 4. Fix hacky left alignment on contact line
% 5. Remove Hacky fix for awkward extra vertical space
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the vertical limit.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%Icons:
%%Main: https://icons8.com/icons/carbon-copy
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{plushcv}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Sakshamdeep}{Singh}{Graduate Student, University at Buffalo - SUNY Buffalo}
{\contactline
	{\href{}{Buffalo, NY}}
	{\href{https://www.github.com/sakshamsds}{GitHub}}
	{\href{https://www.linkedin.com/in/sakshamdeep-singh/}{LinkedIn}}
	{\href{mailto:ssingh86@buffalo.edu}{ssingh86@buffalo.edu}}
	{\href{tel:+17163039262}{+1(716)303-9262}}}
% {\contactline
% 	{\href{}{Buffalo, NY}}
% 	{\href{https://www.github.com/sakshamsds}{saksham}}
% 	{\href{https://www.linkedin.com/in/sakshamdeep-singh/}{saksham.sds}}
% 	{\href{mailto:ssingh86@buffalo.edu}{ssingh86@buffalo.edu}}
% 	{\href{tel:+17163039262}{+1(716)303-9262}}}

% \namesection{Firstname}{Lastname}{Full Stack Software Engineer}{\contactline{\href{https://www.mazumder.me}{mazumder.me}}{\href{https://www.github.com/sansquoi}{sansquoi}}{\href{https://www.linkedin.com/mazumders}{mazumders}}{\href{mailto:shubham.mazumder@gmail.com}{first.last@email.com}}{\href{tel:+1999999999}{9999999999}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.70\textwidth} 
	
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%     EXPERIENCE
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	
	\section{Experience}
	\runsubsection{Wipro Limited}
	\descript{| Project Engineer}
	\location{July 2019 – Aug 2022 | Bengaluru, India}
	\vspace{\topsep} % Hacky fix for awkward extra vertical space
	\begin{tightemize}
		\sectionsep
		\item Worked on Cisco Kinetic Cities. An IoT smart cities project in which I work as Java back-end developer. 
		\item Main focus was on modern application development including micro-services architecture, distributed computing and low latency messaging applications.
		\item Hands-on experience in working on technologies such as Java, Springboot, Python, PostgreSQL, Elasticsearch, Kafka, WSO2, Linux servers.  
	\end{tightemize}
	\sectionsep
	
	\runsubsection{UST Global}
	\descript{| Software Development Intern }
	\location{July 2018 – December 2018 | Trivandrum, India}
	\begin{tightemize}
		\sectionsep
		\item Successfully developed REST APIs using SpringBoot. 
		\item  As a part of the Sentiment Analysis Team, helped in data extraction from Facebook and Twitter, and learned to analyze sentiments using various approaches.
	\end{tightemize}
	\sectionsep
	
	\runsubsection{Ultratech Limited}
	\descript{| Research Intern }
	\location{May 2017 – July 2017 | Reddipalayam, India}
	\begin{tightemize}
		\sectionsep
		\item Ran first-hand study of the industrial cement manufacturing plant and covered processes, applications and automation tools used in the end to end process.
	\end{tightemize}
	\sectionsep
	
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%     Projects
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	
	\section{Projects}
	
	\runsubsection{Research Paper Implementation}
	\descript{| Python + PyTorch}
	\location{March 2019 - April 2019}
	\begin{tightemize}
		\item Implemented the following IEEE paper as part of the the NNFL course project. "Facial Expression Recognition Using Weighted Mixture Deep Neural Network Based on Double-Channel Facial Images"
	\end{tightemize}
	\sectionsep
	
	\runsubsection{Created fake images using GAN's}
	\descript{| Python + PyTorch}
	\location{July 2019}
	\begin{tightemize}
		\item Implemented and trained GAN's model on CIFAR-10 data set to create a set of fake images.
	\end{tightemize}
	\sectionsep
	
	\runsubsection{Vehicle detection with YOLOv2}
	\descript{| Python + Keras}
	\location{Nov 2018}
	\begin{tightemize}
		\item Implemented a YOLO model for car detection using data set provided by drive.ai.
	\end{tightemize}
	\sectionsep
	
	\runsubsection{Emojifier}
	\descript{| Python + Tensorflow}
	\location{Oct 2018}
	\begin{tightemize}
		\item Built two emojifiers that map sentences to appropriate emojis using word embedding and LSTM.
	\end{tightemize}
	\sectionsep
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%     AWARDS
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	
	\section{Awards \& Achievements} 
	\begin{tabular}{rll}
		2020 & Best Performer, Wipro & Awarded at the end of CKC 5.0 project cycle \\
		2015 & 99.45 percentile      & JEE Mains, among 1.3 million candidates     \\
		2014 & Silver Medal          & Mathematics Olympiad, School Rank, $2^{nd}$ \\
		\\
	\end{tabular}
	\sectionsep
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	%     COLUMN TWO
	%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	
\end{minipage} 
\hfill
\begin{minipage}[t]{0.25\textwidth} 
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%     EDUCATION
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	
	\section{Education} 
	
	\subsection{University at Buffalo}
	\descript{MS Artificial Intelligence}
	\location{Aug 2022 - Dec 2023 | Buffalo, NY}
	\sectionsep
	
	\subsection{BITS Pilani}
	\descript{B.E.(Hons.) Electronics and Instrumentation}
	\location{Aug 2015 - May 2019 | Pilani, India}
	% \location{ Cum. GPA: 5.92 / 10.0 }
	\sectionsep
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%     SKILLS
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	
	\section{Skills}
	\subsection{Languages}
	\sectionsep
	Java \textbullet{} Python \textbullet{} SQL \textbullet{} R \textbullet{} JS\\
	\sectionsep
	\sectionsep
	
	\subsection{Databases/Pipelines}
	\sectionsep
	PostgreSQL \textbullet{} MongoDB \textbullet{} ElasticSearch \textbullet{} Apache Kafka \textbullet{} RabbitMQ \\
	\sectionsep
	\sectionsep
	
	\subsection{Frameworks/Libraries}
	\sectionsep
	SpringBoot \textbullet{} PyTorch \textbullet{} Keras \textbullet{} TensorFlow \textbullet{} NumPy \textbullet{} Pandas \textbullet{} Scikit-Learn\\
	\sectionsep
	
	
	% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	% %     REFERENCES
	% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%     COURSEWORK
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	
	\section{Coursework}
	
	\subsection{Computer Science}
	C Programming \textbullet{}\\ 
	Object Oriented Programming \textbullet{}\\ 
	Operating Systems 
	\sectionsep
	
	\subsection{Mathematics}
	Mathematics I, II, III \textbullet{}\\
	Probability and Statistics \textbullet{}\\
	Number Theory
	\sectionsep
	 
	\subsection{Online Courses}
	Machine Learning \textbullet{}\\ 
	Deep Learning Specialization \textbullet{}\\ 
	The Analytics Edge 
	\sectionsep
	
	 
	\section{Extracurricular}
	\subsection{Student Mentor, NSS}
	NSS helps in providing hands-on experience to young students in delivering community service.
	 
	
	
\end{minipage} 
\end{document}  \documentclass[]{article}